---
title: \texttt{immunoSeqR} Analysis
#author: "Alex Hopkins"
output: pdf_document
header-includes:
   - \usepackage{graphicx}

---
# Adjuvant Study
Created `r  format(Sys.Date(),"%m/%d/%y")`

```{r eval=TRUE,echo=FALSE}
require(immunoSeqR)
require(ggplot2)
require(gridExtra)
require(knitr)
require(reshape2)
require(rmarkdown)
r <- 
function(){render('~/Documents/emj/ImmunoseqResults/immunoSeqR/scripts/rmd/adjuvant.Rmd',output_file=
'~/Documents/emj/ImmunoseqResults/new/adjuvant.pdf')}
first_run <- TRUE
verbose=FALSE

```
```{r eval=first_run}
dict <- readRDS('~/Documents/emj/ImmunoseqResults/data/adjuvant/dict.Rds')
stats <- readRDS('~/Documents/emj/ImmunoseqResults/data/adjuvant/stats.Rds')
plot_ds <- readRDS('~/Documents/emj/ImmunoseqResults/data/adjuvant/plot_ds.Rds')
load('~/Documents/emj/ImmunoseqResults/data/adjuvant/olm.Rda')
load('~/Documents/emj/ImmunoseqResults/data/adjuvant/sum.ds.Rda')

#Filter one bad sample
w <- which(plot_ds$patient=='3.026' & plot_ds$type=='PDAC')
plot_ds <- plot_ds[-w,]
```


## Background
\includegraphics[width=\textwidth]{/home/ahopkins/Documents/emj/figures/J9988_timeline.pdf}

### Dataset
The data set contains `r sum.ds$nsamp` samples, of `r  sum.ds$ntypes` types.
There are `r  sum.ds$unique.tcr` unique TCRs, collapsed from `r  sum.ds$total.tcr` distinct
productive CDR3 sequences. This represents an average synonymity of `r  sum.ds$avg.syn`.
The maximum synonymity (in the parent data set) was `r  sum.ds$max.syn` (clone sequence `r
sum.ds$max.syn.aa `).\par


### Metadata  
The available metadata fields in the dictionary are: `r paste(names(dict)[-1],collapse=', ')`. The statistics computed are `r paste(names(stats)[names(stats)!='fn'],collapse=', ')`.

\clearpage


### By Response

```{r by_response,echo=verbose,fig.align='center'}
x_val <- 'response'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
	l <- vector('list')
	for(a in types){
	    l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
	}
	do.call(grid.arrange,c(l,ncol=length(types)))
}
```

\clearpage

### Change in Metrics

```{r delta_metrics,eval=TRUE,echo=verbose,}
w <- grep('Log',names(plot_ds))
l <- vector('list')
for(a in seq(length(w))){
  l[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'response','POST') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST')
}
do.call(grid.arrange,c(l,ncol=length(w)))
````
\clearpage

### By Type
```{r by_type,echo=verbose,fig.align='center'}
metrics <- names(stats[names(stats)!='fn'])
l <- vector('list')
for(b in metrics){
        l[[b]] <- iseqr_plot_factor(plot_ds,b,'type',NA) + theme(axis.text=element_text(size=5))
}
    do.call(grid.arrange,c(l,ncol=length(types)))

```
\clearpage

## Overlaps

```{r overlap,echo=verbose,eval=TRUE,fig.align='center',fig.height=8}
rownames(mm) <- paste0(dict$patient,dict$type)
colnames(mm) <- rownames(mm)
w <- c(which(dict$response=='NR'),which(dict$response=='R'))
tdict <- dict[w,]
tmm <- mm[w,w]
tmm.m <- melt(tmm)
g <- ggplot(tmm.m,aes(x=Var1,y=Var2)) +
    geom_tile(aes(fill=value)) +
    coord_fixed() +
    scale_fill_gradient(low='white',high='black')+
    theme(axis.text=element_text(size=5,colour=tdict$response),
            axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
    xlab('') + ylab('') + ggtitle('Morisita Overlap')
g
```
\clearpage

## Expanded Clones
```{r, expanded_clones,echo=verbose,eval=TRUE,fig.width=4}
w <- grep('Number of Expanded',names(plot_ds))
iseqr_plot_factor(plot_ds,names(plot_ds)[w],'response',type='POST')

```
```{r exp_cl_vs_Tumor, eval=FALSE,echo=verbose}
mats <- out$total
patients <- names(mats)
resp <- sapply(patients,FUN=iseqr_lookup,dict=dict)
mats <- mats[order(resp)]
patients <- patients[order(resp)]
resp <- resp[order(resp)]
nr <- length(which(resp=='NR'))
r <- length(which(resp=='R'))
layout <- matrix(nrow=max(r,nr),ncol=2)
layout[seq(nr),1] <- seq(nr)
layout[,2] <- seq(r)+nr

plots <- list()
for(a in seq_along(mats)){
    tds <- as.data.frame(mats[[a]])
    w <- which(dict$patient==patients[a] & dict$type=='PDAC')
    tds[,4] <- ds_nt[,w]
    names(tds)[4] <- 'PDAC'
    #calculate the lfc
    ttds <- tds
    ttds[ttds[,1]==0,1] <- 1
    ttds[ttds[,2]==0,2] <- 1
    tds$lfc <- log(ttds[,2]/ttds[,1],2)
    rm(ttds)
    #
    lowest <- min(tds$p_adj[tds$p_adj>0]) # lowest non-0 p-val
    tds$p_adj[tds$p_adj==0] <- lowest # clip any p=0 to next lowest
    tds <- tds[which(tds$PDAC>0),] # restrict to tumor
    suppressWarnings(
        l <- max(abs(-log(tds$p_adj,10))) # plot limit
    )
    if(l<1.3){l <- 1.3} # minimum of -log(0.05,10)
    sh <- shared(tds$PDAC,rowSums(tds[,c(1,2)]))
    if(nrow(tds)>0){
        plots[[a]] <- ggplot(tds,aes(x=-log(p_adj,10),y=PDAC,color=lfc)) +
            geom_point() + theme_bw()+
            ylab('Tumor Counts') +
            xlab('-log(p)') +
            ggtitle(paste0(patients[a],'(',resp[a],')',' ',sh,' ','shared')) +
            scale_colour_gradient2(low='red',mid='black',high='green',midpoint=0)+
            scale_x_continuous(limits=c(0,l))
    }else{
			plots[[a]] <- suppressWarnings(ggplot() + geom_blank()+
							ggtitle(paste0(patients[a],'(',resp[a],')',' ',sh,' ','shared'))
						)
	}
}
g <- grid.arrange(grobs=plots,layout_matrix=layout)
ggsave(g,file='~/Desktop/test_fixed_adj.pdf',height=2*nrow(layout),width=8)
```

\clearpage

## Confounders

### Age

```{r echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5,width=8}
x_val <- 'age'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a,sm=TRUE)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
	cat('  \n')
}
```

### Cell Number

```{r echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5,fig.width=8}
x_val <- 'cells'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types[types!='PDAC']){
        l[[a]] <- iseqr_plot_metrics(plot_ds[!is.na(plot_ds$cells),],b,x_val,a) + 
					theme(axis.text=element_text(size=5))
    }
    do.call(grid.arrange,c(l,ncol=length(types)))  
	cat('  \n')
}
```
