---
output: pdf_document
header-includes:
   - \usepackage{graphicx}
---
# \texttt{immunoSeqR} Analysis
Created `r  format(Sys.Date(),"%m/%d/%y")`

```{r eval=TRUE,echo=FALSE}
require(immunoSeqR)
require(ggplot2)
require(gridExtra)
r <- function(){render('~/Documents/emj/ImmunoseqResults/immunoSeqR/scripts/mega_analysis.Rmd',output_dir='~/Desktop/out/')}
first_run <- TRUE
```
```{r eval=TRUE, cache=!first_run}
load('~/Documents/emj/ImmunoseqResults/mega/ds_agg.Rda')
load('~/Documents/emj/ImmunoseqResults/mega/dict.Rda')
load('~/Documents/emj/ImmunoseqResults/mega/stats.Rda')
```
```{r eval=TRUE,echo=FALSE}
total_ds <- ds
total_dict <- dict
total_stats <- stats
rm(ds)
rm(dict)
gc()
```
## Background
### Dataset


The data set contains `r ncol(total_ds)-2` samples, of `r length(levels(total_dict$type))` types. 
There are `r format(nrow(total_ds),big.mark=',')` unique TCRs, collapsed from `r format(sum(total_ds$syn),big.mark=',')` distinct productive CDR3 sequences. This represents an average synonymity of `r summary(total_ds$syn)['Mean']`. The maximum synonymity was `r summary(total_ds$syn)['Max.']` (clone sequence `r total_ds$aa[which.max(total_ds$syn)]`).\par

### Metadata  
The available metadata fields in the total_dictionary are: `r paste(names(total_dict)[-1],collapse=', ')`. The statistics computed are `r paste(names(stats)[names(stats)!='fn'],collapse=', ')`.

\clearpage




## Neoadjuvant Study
\includegraphics[width=\textwidth]{/home/ahopkins/Documents/emj/figures/J0810_timeline.pdf}

```{r eval=TRUE,echo=FALSE}
ds <- total_ds[,c(1,2,which(total_dict$experiment=='Neoadjuvant'))]
dict <- total_dict[which(total_dict$experiment=='Neoadjuvant'),]
dict <- refactor(dict)
stats <- total_stats[which(total_dict$experiment=='Neoadjuvant')-2,]
plot_ds <- merge(dict,stats)
```
`r ncol(ds)-2` samples, of `r length(levels(dict$type))` types.

```{r echo=FALSE}
x_val <- 'response'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
	l <- vector('list')
	for(a in types){
	    l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a)
	}
	do.call(grid.arrange,c(l,ncol=length(types)))
}
```



## Adjuvant Study
\includegraphics[width=\textwidth]{/home/ahopkins/Documents/emj/figures/J9988_timeline.pdf}

```{r eval=TRUE,echo=FALSE}
ds <- total_ds[,c(1,2,which(total_dict$experiment=='Adjuvant'))]
dict <- total_dict[which(total_dict$experiment=='Adjuvant'),]
suppressWarnings(dict <- refactor(dict))
stats <- total_stats[which(total_dict$experiment=='Adjuvant')-2,]
plot_ds <- merge(dict,stats)
```
`r ncol(ds)-2` samples, of `r length(levels(dict$type))` types.

```{r echo=FALSE}
x_val <- 'response'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
}
```
## Adjuvant-Neoadjuvant Comparison
```{r eval=TRUE,echo=FALSE}
dict <- total_dict[which(total_dict$experiment=='Adjuvant|Neoadjuvant'),]
dict <- refactor(dict)
stats <- total_stats[which(total_dict$experiment=='Adjuvant|Neadjuvant')-2,]
plot_ds <- merge(dict,stats)
```



## SBRT Study

```{r eval=TRUE,echo=FALSE}
ds <- total_ds[,c(1,2,which(total_dict$experiment=='SBRT'))]
dict <- total_dict[which(total_dict$experiment=='SBRT'),]
dict <- refactor(dict)
stats <- total_stats[which(total_dict$experiment=='SBRT')-2,]
plot_ds <- merge(dict,stats)
```
`r ncol(ds)-2` samples, of `r length(levels(dict$type))` types.


```{r echo=FALSE}
x_val <- 'arm'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
}
```

