---
title: \texttt{immunoSeqR} Analysis
#author: "Alex Hopkins"
output: pdf_document
geometry: margin=0.75in
header-includes:
   - \usepackage{graphicx}
---
# Anti-CTLA4 + GVAX Study
Created `r  format(Sys.Date(),"%m/%d/%y")`

```{r eval=TRUE,echo=FALSE}
require(immunoSeqR)
require(ggplot2)
require(gridExtra)
require(reshape2)
require(knitr)
require(rmarkdown)
first_run <- FALSE
verbose=FALSE
r <- function(){render('~/Documents/emj/ImmunoseqResults/immunoSeqR/scripts/rmd/ipi.Rmd',
output_file='~/Documents/emj/ImmunoseqResults/new/ipi.pdf',
intermediates_dir='~/Documents/emj/ImmunoseqResults/new/')}
```
```{r eval=first_run}
ds <- readRDS('~/Documents/emj/ImmunoseqResults/ipi/ds_agg_ipi.Rds')
dict <- readRDS('~/Documents/emj/ImmunoseqResults/ipi/dict_ipi.Rds')
stats <- readRDS('~/Documents/emj/ImmunoseqResults/ipi/stats_ipi.Rds')
load('~/Documents/emj/ImmunoseqResults/ipi/olm_ipi.Rda')
load('~/Documents/emj/ImmunoseqResults/ipi/sum.ds_ipi.Rda')
```

## Background
\includegraphics[width=\textwidth]{/home/ahopkins/Documents/emj/figures/J0834_timeline.pdf}

### Dataset

The data set contains `r sum.ds$nsamp` samples, of `r  sum.ds$ntypes` types. 
There are `r  format(sum.ds$unique.tcr,big.mark=',')` unique TCRs, collapsed from `r  
format(sum.ds$total.tcr,big.mark=',')` distinct productive CDR3 sequences. This represents an 
average synonymity of `r  round(sum.ds$avg.syn,3)`. The maximum synonymity (in the parent data 
set) was `r sum.ds$max.syn` (clone sequence `r sum.ds$max.syn.aa `).\par

### Metadata  
The available metadata fields in the dictionary are: `r paste(names(dict)[-1],collapse=', ')`. The statistics computed are `r paste(names(stats)[names(stats)!='fn'],collapse=', ')`.

\clearpage


### By Response

```{r eval=TRUE,echo=verbose,cache=FALSE}
#put sum of seqs at the end
#stats <- stats[,c(1,3,2,4)]
plot_ds <- merge(dict,stats)
```
```{r by_response,echo=verbose,fig.align='center'}
x_val <- 'response'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
	l <- vector('list')
	for(a in types){
	    l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
	}
	do.call(grid.arrange,c(l,ncol=length(types)))
}
```
\clearpage

#By Adverse Event Status
\textbf{Yes} indicates that the patient experienced a non-skin immune related adverse event of 
any grade. 

```{r by_ae,echo=verbose,fig.align='center'}
x_val <- 'nonskin.irae'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
  l <- vector('list')
  for(a in types){
      l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
  }
  do.call(grid.arrange,c(l,ncol=length(types)))
}
```

\clearpage

### By Type
```{r by_type,echo=verbose,fig.align='center'}
metrics <- names(stats[names(stats)!='fn'])
l <- vector('list')
for(b in metrics){
        l[[b]] <- iseqr_plot_factor(plot_ds,b,'type',NA) + theme(axis.text=element_text(size=5))
}
    do.call(grid.arrange,c(l,ncol=length(types)))

```
\clearpage

### By Treatment Arm

\begin{center}
\begin{tabular}{l l}
Arm 1 & Ipilimumab \\
Arm 2 & Ipilimumab + Cy + GVAX \\
\end{tabular}
\end{center}


```{r echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5}
x_val <- 'arm'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
}
```
\clearpage




## Overlaps

```{r overlap,echo=verbose,eval=TRUE,fig.align='center',fig.height=8}
rownames(mm) <- paste0(dict$patient,dict$type)
colnames(mm) <- rownames(mm)
w <- c(which(dict$response=='NR'),which(dict$response=='R'))
tdict <- dict[w,]
tmm <- mm[w,w]
tmm.m <- melt(tmm)
g <- ggplot(tmm.m,aes(x=Var1,y=Var2)) +
    geom_tile(aes(fill=value)) +
    coord_fixed() +
    scale_fill_gradient(low='white',high='black',na.value='white')+
    theme(axis.text=element_text(size=5,colour=tdict$response),
            axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
    xlab('') + ylab('') + ggtitle('Morisita Overlap')
g
```
\clearpage


## Expanded Clones
```{r expanded_clones,echo=verbose,eval=FALSE}
#rm(ds)
#ds_nt <- readRDS('~/Documents/emj/ImmunoseqResults/ipi/fixed/ds_ipi_fixed.Rds')
```
```{r calc_exp_cl,echo=verbose,cache=TRUE}
#out <- iseqr_exp_cl(ds_nt,dict)
#out <- readRDS('~/Documents/emj/ImmunoseqResults/ipi/fixed/exp_cl_out_nadj.Rds')
```
```{r exp_cl_plot, echo=verbose,fig.align='center',fig.height=3,fig.width=5}
#resp <- sapply(names(out$num_exp),FUN=iseqr_lookup,dict=dict)
#arm <- sapply(names(out$num_exp),FUN=iseqr_lookup,dict=dict,o_col='arm')
#df <- data.frame(patient=names(out$num_exp),response=resp,arm=arm,num_exp=out$num_exp)
#g <- iseqr_plot_factor(df,'num_exp','response',NA)
#g <- g + ylab('Number of Expanded Clones')
#f <- iseqr_plot_factor(df,'num_exp','arm',NA)
#f <- f + ylab('Number of Expanded Clones')
#grid.arrange(g,f,ncol=2)

```

\clearpage

## Confounders

### Age

```{r by_age,echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5}
x_val <- 'age'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a,sm=TRUE)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
	cat('  \n')
}
```
\clearpage

### Cell Number

```{r by_cell_num,echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5,fig.width=8}
#x_val <- 'cells'
#metrics <- names(stats[names(stats)!='fn'])
#types <- levels(plot_ds$type)
#for(b in metrics){
#    l <- vector('list')
#    for(a in types[types!='PDAC']){
#        l[[a]] <- iseqr_plot_metrics(plot_ds[!is.na(plot_ds$cells),],b,x_val,a) + #
#					theme(axis.text=element_text(size=5))
#    }
#    do.call(grid.arrange,c(l,ncol=length(types)))  #
#	cat('  \n')
#}
```
