---
title: \texttt{immunoSeqR} Analysis
#author: "Alex Hopkins"
output: pdf_document
geometry: margin=0.75in
header-includes:
   - \usepackage{graphicx}
---
# Anti-CTLA4 + GVAX Study
Created `r  format(Sys.Date(),"%m/%d/%y")`

```{r eval=TRUE,echo=FALSE}
require(immunoSeqR)
require(ggplot2)
require(gridExtra)
require(reshape2)
require(knitr)
require(rmarkdown)
first_run <- FALSE
verbose=FALSE
r <- function(){render('~/Documents/emj/ImmunoseqResults/immunoSeqR/scripts/rmd/ipi.Rmd',
output_file='~/Documents/emj/ImmunoseqResults/new/ipi.pdf',
intermediates_dir='~/Documents/emj/ImmunoseqResults/new/')}
```
```{r eval=first_run}
dict <- readRDS('~/Documents/emj/ImmunoseqResults/data/ipi/dict.Rds')
stats <- readRDS('~/Documents/emj/ImmunoseqResults/data/ipi/stats.Rds')
plot_ds <- readRDS('~/Documents/emj/ImmunoseqResults/data/ipi/plot_ds.Rds')
load('~/Documents/emj/ImmunoseqResults/data/ipi/olm.Rda')
load('~/Documents/emj/ImmunoseqResults/data/ipi/sum.ds.Rda')
```

## Background
\includegraphics[width=\textwidth]{/home/ahopkins/Documents/emj/figures/J0834_timeline.pdf}

### Dataset

The data set contains `r sum.ds$nsamp` samples, of `r  sum.ds$ntypes` types. 
There are `r  format(sum.ds$unique.tcr,big.mark=',')` unique TCRs, collapsed from `r  
format(sum.ds$total.tcr,big.mark=',')` distinct productive CDR3 sequences. This represents an 
average synonymity of `r  round(sum.ds$avg.syn,3)`. The maximum synonymity (in the parent data 
set) was `r sum.ds$max.syn` (clone sequence `r sum.ds$max.syn.aa `).\par

### Metadata  
The available metadata fields in the dictionary are: `r paste(names(dict)[-1],collapse=', ')`. The statistics computed are `r paste(names(stats)[names(stats)!='fn'],collapse=', ')`.

\clearpage


### By Response


```{r by_response,echo=verbose,fig.align='center'}
x_val <- 'response'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
	l <- vector('list')
	for(a in types){
	    l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
	}
	do.call(grid.arrange,c(l,ncol=length(types)))
}
```
\clearpage

## Change In Metrics
```{r delta_metrics,eval=TRUE,echo=verbose}
w <- grep('Log',names(plot_ds))
l <- vector('list')
m <- vector('list')
for(a in seq(length(w))){
  l[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'response','POST1') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST1')
  m[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'response','POST3') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST3')
}
do.call(grid.arrange,c(l,ncol=length(w)))
cat('\n\n')
do.call(grid.arrange,c(m,ncol=length(w)))
```

\clearpage

#By Adverse Event Status
\textbf{Yes} indicates that the patient experienced a non-skin immune related adverse event of 
any grade. 

```{r by_ae,echo=verbose,fig.align='center'}
x_val <- 'nonskin.irae'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
  l <- vector('list')
  for(a in types){
      l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
  }
  do.call(grid.arrange,c(l,ncol=length(types)))
}
```

\clearpage

## Change In Metrics
```{r delta_metrics_ae,eval=TRUE,echo=verbose,}
w <- grep('Log',names(plot_ds))
l <- vector('list')
m <- vector('list')
for(a in seq(length(w))){
  l[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'nonskin.irae','POST1') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST1')
  m[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'nonskin.irae','POST3') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST3')
}
do.call(grid.arrange,c(l,ncol=length(w)))
cat('\n\n')
do.call(grid.arrange,c(m,ncol=length(w)))
```


\clearpage

### By Type
```{r by_type,echo=verbose,fig.align='center'}
metrics <- names(stats[names(stats)!='fn'])
l <- vector('list')
for(b in metrics){
        l[[b]] <- iseqr_plot_factor(plot_ds,b,'type',NA) + theme(axis.text=element_text(size=5))
}
    do.call(grid.arrange,c(l,ncol=length(types)))

```
\clearpage

### By Treatment Arm

\begin{center}
\begin{tabular}{l l}
Arm 1 & Ipilimumab \\
Arm 2 & Ipilimumab + Cy + GVAX \\
\end{tabular}
\end{center}


```{r echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5}
x_val <- 'arm'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
}
```
\clearpage

## Change In Metrics
```{r delta_metrics_arm,eval=TRUE,echo=verbose,}
w <- grep('Log',names(plot_ds))
l <- vector('list')
m <- vector('list')
for(a in seq(length(w))){
  l[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'arm','POST1') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST1')
  m[[a]] <- iseqr_plot_factor(plot_ds,names(plot_ds)[w[a]],'arm','POST3') +
                              geom_hline(yintercept=0,alpha=0.1) + ggtitle('PRE to POST3')
}
do.call(grid.arrange,c(l,ncol=length(w)))
cat('\n\n')
do.call(grid.arrange,c(m,ncol=length(w)))
```



## Overlaps

```{r overlap,echo=verbose,eval=TRUE,fig.align='center',fig.height=8}
rownames(mm) <- paste0(dict$patient,dict$type)
colnames(mm) <- rownames(mm)
w <- c(which(dict$response=='NR'),which(dict$response=='R'))
tdict <- dict[w,]
tmm <- mm[w,w]
tmm.m <- melt(tmm)
g <- ggplot(tmm.m,aes(x=Var1,y=Var2)) +
    geom_tile(aes(fill=value)) +
    coord_fixed() +
    scale_fill_gradient(low='white',high='black',na.value='white')+
    theme(axis.text=element_text(size=5,colour=tdict$response),
            axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))+
    xlab('') + ylab('') + ggtitle('Morisita Overlap')
g
```
\clearpage


## Expanded Clones
```{r exp_cl_plot, echo=verbose,fig.align='center',fig.height=4,fig.width=7}
w <- grep('Number of Expanded',names(plot_ds))
g <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'response',type='POST1') + xlab('Response')
f <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'arm',type='POST1') + xlab('Arm')
h <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'nonskin.irae',type='POST1') + xlab('AE')
grid.arrange(g,f,h,ncol=3)

w <- grep('Number of Expanded',names(plot_ds))
g <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'response',type='POST3') + xlab('Response')
f <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'arm',type='POST3') + xlab('Arm')
h <- iseqr_plot_factor(plot_ds,names(plot_ds)[w],'nonskin.irae',type='POST3') + xlab('AE')
grid.arrange(g,f,h,ncol=3)


```

\clearpage

## Confounders

### Age

```{r by_age,echo=verbose,cache=FALSE,fig.align='center',fig.height=2.5}
x_val <- 'age'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_metrics(plot_ds,b,x_val,a,sm=TRUE)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
	cat('  \n')
}
```
\clearpage

