---
title: \texttt{immunoSeqR} Analysis
#author: "Alex Hopkins"
output: pdf_document
header-includes:
   - \usepackage{graphicx}

---
# SBRT Study
Created `r  format(Sys.Date(),"%m/%d/%y")`

```{r eval=TRUE,echo=FALSE}
require(immunoSeqR)
require(ggplot2)
require(gridExtra)
require(knitr)
first_run <- FALSE
verbose=FALSE

```
```{r eval=first_run}
load('~/Documents/emj/ImmunoseqResults/mega/ds_agg.Rda')
load('~/Documents/emj/ImmunoseqResults/mega/dict.Rda')
load('~/Documents/emj/ImmunoseqResults/mega/stats.Rda')
```
```{r eval=first_run,echo=verbose,warn=FALSE}
if(!all(unlist(iseqr_check(ds,dict,stats)))){stop('Check dictionary and stats.')}
w <- which(dict$experiment=='SBRT')
ds <- ds[,c(w,1,2)] # put syn and aa on the end, then dictionary does not need to be padded
ds <- iseqr_clean_ds(ds)
stats <- stats[w-2,]
dict <- dict[w,] # will result in an unpadded dictionary, but will work with new ds
dict <- refactor(dict)
if(!all(unlist(iseqr_check(ds,dict,stats)))){stop('Error collapsing dictionary or stats.')}
gc <- gc()
```
## Background

### Dataset

The data set contains `r ncol(ds)-2` samples, of `r length(levels(dict$type))` types. 
There are `r format(nrow(ds),big.mark=',')` unique TCRs, collapsed from `r 
format(sum(ds$syn),big.mark=',')` distinct productive CDR3 sequences. This represents an average 
synonymity of `r summary(ds$syn)['Mean']`. The maximum synonymity (in the parent data set) was `r 
summary(ds$syn)['Max.']` (clone sequence `r ds$aa[which.max(ds$syn)]`).\par

### Metadata  
The available metadata fields in the dictionary are: `r paste(names(dict)[-1],collapse=', ')`. The statistics computed are `r paste(names(stats)[names(stats)!='fn'],collapse=', ')`.

\clearpage


### By Type

```{r eval=TRUE,echo=verbose,cache=FALSE}
#put sum of seqs at the end
stats <- stats[,c(1,3,2,4)]
plot_ds <- merge(dict,stats)

```
```{r echo=verbose,fig.align='center'}
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
l <- vector('list')
for(b in metrics){
	    l[[b]] <- iseqr_plot_factor(plot_ds,b,'type',NA) + theme(axis.text=element_text(size=5))
}
do.call(grid.arrange,c(l,ncol=length(types)))
```
```{r echo=FALSE,results='asis'}
for(a in metrics){
	print(kable(iseqr_summarize(plot_ds,'type',metric=a),
		format='markdown',
		digits=3,
		align='c'))
}
```

\clearpage

### By Treatment Arm
```{r echo=verbose,fig.align='center'}
x_val <- 'arm'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types){
        l[[a]] <- iseqr_plot_factor(plot_ds,b,x_val,a)
    }
    do.call(grid.arrange,c(l,ncol=length(types)))
}
```
\clearpage

## Confounders

### Cell Number

```{r echo=verbose,cache=FALSE,fig.align='center',fig.height=3,fig.width=8}
x_val <- 'cells'
metrics <- names(stats[names(stats)!='fn'])
types <- levels(plot_ds$type)
for(b in metrics){
    l <- vector('list')
    for(a in types[types!='PDAC']){
        l[[a]] <- iseqr_plot_metrics(plot_ds[!is.na(plot_ds$cells),],b,x_val,a) + 
					theme(axis.text=element_text(size=5))
    }
    do.call(grid.arrange,c(l,ncol=length(types)))  
	cat('  \n')
}
```
